### 2019-02-20 appendices/proofs.tex
restructure appendices
Overhaul of proof appendix

\section{Appendix}

  \subsection{Evaluation rules}

  % \begin{figure}

    \begin{gather*}
      \boxed{\RelationE} \Break
      \userule{E-Value} \Break
      \userule{E-App} \Break
      \userule{E-IfTrue} \Break
      \userule{E-IfFalse} \Break
      \userule{E-Pair} \Break
      \userule{E-Ref} \Quad
      \userule{E-Deref} \Break
      \userule{E-Assign} \Break
      \userule{E-Edit} \Quad
      \userule{E-Enter} \Quad
      \userule{E-Update} \Break
      \userule{E-Then} \Quad
      \userule{E-Next} \Break
      \userule{E-And} \Quad
      \userule{E-Or} \Break
      \userule{E-Xor} \Quad
      \userule{E-Appoint} \Quad
      \userule{E-Fail}
    \end{gather*}

  %   \caption{Evaluation semantics} \label{fig:evaluation-semantics}
  % \end{figure}

  \subsection{Additional typing rules}

  % \begin{figure}[h]

    \begin{gather*}
      \boxed{\RelationT} \Break
      \userule{T-Var} \Quad
      \userule{T-Loc} \Break
      \userule{T-Abs} \Quad
      \userule{T-App} \Break
      \userule{T-If} \Break
      \userule{T-Pair} \Break
      \userule{T-Ref} \Quad
      \userule{T-Deref} \Break
      \userule{T-Assign}
    \end{gather*}

  %   \caption{Additional typing rules}
  % \end{figure}

  \subsection{Proofs}

  \subsubsection{Theorem~\ref{thm:pres-eval}}
\begin{proof}
  We prove Theorem~\ref{thm:pres-eval} by induction on $e$:\\

  \noindent\textbf{Case} $e=\lambda x:\tau.e, e_1 e_2, x, c, l, e_1 \star e_2,
      \If{e_1}{e_2}{e_3},$\\
      $\tuple{e_1, e_2},\unit,\Ref e,!e,e_1 := e_2$ preservation has
      been proven for these cases by Pierce~\cite{books/Pierce02TAPL}.\\

  \noindent\textbf{Case} $\userule{E-Edit}$\\
    \indent Given that $\Gamma,\Sigma\infers\Edit e:\Task \tau$ and $\Sigma\infers s$,
      \refrule{T-Edit} gives us that $\Gamma,\Sigma\infers e:\tau$. The induction
      hypothesis gives us that $e,s\evaluate v,s'$ also preserves, and thus
      $\Gamma,\Sigma\infers v:\tau$ and $\Sigma\infers s'$. Therefore
      $\Gamma,\Sigma\infers\Edit v:\Task\tau$.\\

  \noindent\textbf{Case} $\userule{E-Enter}$\\
    \indent Evaluation does not alter $e$ and $s$, therefore this case holds tivially.\\

  \noindent\textbf{Case} $\userule{E-Update}$\\
    \indent Given that $\Gamma,\Sigma\infers \Edit e:\Task \tau$ and
      $\Sigma\infers s$, \refrule{T-Update} gives us that $\Gamma,\Sigma\infers e:\Ref \tau$.
      The induction hypothesis gives us that $e,s\evaluate l,s'$ also preserves,
      and thus $\Gamma,\Sigma\infers l:\Ref\tau$ and $\Sigma\infers s'$.
      Therefore $\Gamma,\Sigma\infers\Update l:\Task\tau$\\

  \noindent\textbf{Case} $\userule{E-Fail}$\\
    \indent Evaluation does not alter $e$ and $s$, therefore this case holds tivially.\\

  \noindent\textbf{Case} $\userule{E-Then}$\\
    \indent Given that $\Gamma,\Sigma\infers e_1\Then e_2:\Task \tau$ and
      $\Sigma\infers s$, \refrule{T-Then} gives us that
      $\Gamma,\Sigma\infers e_1:\Task\tau_1$ and
      $\Gamma,\Sigma\infers e_2:\tau_1 \to \Task \tau$. By the induction
      hypothesis, we know that $e_1,s\evaluate t_1,s'$ preserves and thus
      $\Gamma,\Sigma\infers t_1:\Task\tau_1$ and $\Sigma\infers s'$. Therefore
      $\Gamma,\Sigma\infers t_1\Then e_2:\Task\tau$.\\

  \noindent\textbf{Case} $\userule{E-Next}$\\
    \indent Given that $\Gamma,\Sigma\infers e_1\Next e_2:\Task \tau$ and
      $\Sigma\infers s$, \refrule{T-Next} gives us that
      $\Gamma,\Sigma\infers e_1:\Task\tau_1$ and
      $\Gamma,\Sigma\infers e_2:\tau_1 \to \Task \tau$. By the induction
      hypothesis, we know that $e_1,s\evaluate t_1,s'$ preserves and thus
      $\Gamma,\Sigma\infers t_1:\Task\tau_1$ and $\Sigma\infers s'$. Therefore
      $\Gamma,\Sigma\infers t_1\Next e_2:\Task\tau$.\\

  \noindent\textbf{Case} $\userule{E-And}$\\
    \indent  Given that $\Gamma,\Sigma\infers e_1\And e_2:\Task(\tau_1\times\tau_2)$
      and $\Sigma\infers s$, \refrule{T-And} gives us that
      $\Gamma,\Sigma\infers e_1:\Task\tau_1$ and
      $\Gamma,\Sigma\infers e_2:\Task\tau_2$. By the induction hypothesis, we
      know that both $e_1,s\evaluate t_1,s'$ and $e_2,s'\evaluate t_2,s''$
      preserve and thus $\Gamma,\Sigma\infers t_1:\Task\tau_1$,
      $\Sigma\infers s'$, $\Gamma,\Sigma\infers t_2:\Task\tau_2$ and
      $\Sigma\infers s''$. Therfore
      $\Gamma,\Sigma\infers t_1\And t_2:\Task(\tau_1\times\tau_2)$\\

  \noindent\textbf{Case} $\userule{E-Or}$\\
    \indent Given that $\Gamma,\Sigma\infers e_1\Or e_2:\Task\tau$ and $\Sigma\infers s$, \refrule{T-Or} gives us that $\Gamma,\Sigma\infers e_1:\Task\tau$ and
      $\Gamma,\Sigma\infers e_2:\Task\tau$. By the induction hypothesis, we have that both
      $e_1,s\evaluate t_1,s'$ and $e_2,s'\evaluate t_2,s''$ preserve and thus $\Gamma,\Sigma\infers t_1:\Task\tau$, $\Sigma\infers s'$,
      $\Gamma,\Sigma\infers t_2:\Task\tau$ and $\Sigma\infers s''$. Therefore $\Gamma,\Sigma\infers t_1\Or t_2:\Task\tau$.\\

  \noindent\textbf{Case} $\userule{E-Xor}$\\
    \indent Evaluation does not alter $e$ and $s$, therefore this case holds tivially.

@@

\subsubsection{Lemma~\ref{lem:presvalue}}
\begin{proof}
  We prove Lemma~\ref{lem:presvalue} by induction over $e$.\\

  \noindent\textbf{Case} $\Value{(\Edit v,s)}=v$ By T-Edit, if
  $\Gamma,\Sigma\infers \Edit v:\Task\tau$, then $\Gamma,\Sigma\infers v:\tau$.\\

  \noindent\textbf{Case} $\Value{(\Enter \tau,s)}=\bot$ Since this case does not
  lead to a value, the lemma holds trivially.\\

  \noindent\textbf{Case} $\Value{(\Update l,s)}=s(l)$ Given that
  $\Gamma,\Sigma\infers\Update l:\Task \tau$ and $\Sigma\infers s$, we know that
  $\Gamma,\Sigma\infers s(l):\tau$ by definiton.\\

  \noindent\textbf{Case} $\Value{(\Fail,s)}=\bot$ Since this case does not lead
  to a value, the lemma holds trivially.\\

  \noindent\textbf{Case} $\Value{(t_1\Then e_2,s)}=\bot$ Since this case does
  not lead to a value, the lemma holds trivially.\\

  \noindent\textbf{Case} $\Value{(t_2\Next e_2,s)}=\bot$ Since this case does
  not lead to a value, the lemma holds trivially.\\

  \noindent\textbf{Case} $\Value{(t_1\And t_2,s)}=\tuple{v_1, v_2}$ given that
  $\Value{(t_1,s)}=v_1\wedge\Value{(t_2,s)}=v_2$\\ By \refrule{T-And} we have that
  $\Gamma,\Sigma\infers t_1\And t_2:\Task(\tau_1\times\tau_2)$ and
  $\Gamma,\Sigma\infers t_1:\tau_1$ and $\Gamma,\Sigma\infers t_2:\tau_2$. By the
  induction hypothesis, $ \Value{(t_1,s)}=v_1$ and $\Value{(t_2,s)}=v_2$ preserve,
  and thus $\Gamma,\Sigma\infers v_1:\tau_1$ and $\Gamma,\Sigma\infers v_2:\tau_2$.
  This gives us that $\Gamma,\Sigma\infers \tuple{v_1, v_2}:\Task(\tau_1\times\tau_2)$ \\

  \noindent\textbf{Case} $\Value{(t_1\And t_2,s)}=\bot$ given that
  $\neg(\Value{(t_1,s)}=v_1\wedge\Value{(t_2,s)}=v_2)$\\ Since this case does
  not lead to a value, the lemma holds trivially.\\

  \noindent\textbf{Case} $\Value{(t_1\Or t_2,s)}=v_1$ given that
  $\Value{(t_1,s)}=v_1$\\
  By \refrule{T-Or} we have that $\Gamma,\Sigma\infers t_1\Or t_2:\Task\tau$,
  and $\Gamma,\Sigma\infers t_1:\Task\tau$ and
  $\Gamma,\Sigma\infers t_2:\Task\tau$. By the induction hypothesis, we have
  that $\Gamma,\Sigma\infers v_1:\tau$.\\

  \noindent\textbf{Case} $\Value{(t_1\Or t_2,s)}=v_2$ given that
  $\Value{(t_1,s)}=\bot\wedge\Value{(t_2,s)}=v_2$\\
  By \refrule{T-Or} we have that $\Gamma,\Sigma\infers t_1\Or t_2:\Task\tau$,
  and $\Gamma,\Sigma\infers t_1:\Task\tau$ and
  $\Gamma,\Sigma\infers t_2:\Task\tau$. By the induction hypothesis, we have
  that $\Gamma,\Sigma\infers v_2:\tau$.\\

  \noindent\textbf{Case} $\Value{(t_1\Or t_2,s)}=\bot$ given that
  $\Value{(t_1,s)}=\bot\wedge\Value{(t_2,s)}=\bot$\\ Since this case does not
  lead to a value, the lemma holds trivially.\\

  \noindent\textbf{Case} $\Value{(t_1\Xor t_2,s)}=\bot$ Since this case does not
  lead to a value, the lemma holds trivially.

@@

\subsubsection{Theorem~\ref{thm:pres-stride}}
\begin{proof}
  We prove Theorem~\ref{thm:pres-stride} by induction on $e$:\\

  \noindent\textbf{Case} $\userule{S-Fail}$ \\
    \indent  Since this case does not alter the
  expression, the theorem holds trivially.\\

  \noindent\textbf{Case} $\userule{S-Xor}$ \\
    \indent  Since this case does not alter the
  expression, the theorem holds trivially.\\

  \noindent\textbf{Case} $\userule{S-Update}$ \\
    \indent  Since this case does not alter
  the expression, the theorem holds trivially.\\

  \noindent\textbf{Case} $\userule{S-Fill}$ \\
    \indent  Since this case does not alter the
  expression, the theorem holds trivially.\\

  \noindent\textbf{Case} $\userule{S-Edit}$ \\
    \indent  Since this case does not alter the
  expression, the theorem holds trivially.\\

  \noindent\textbf{Case} $\userule{S-And}$ \\
    \indent  Given that
  $\Gamma,\Sigma\infers t_1\And t_2:\Task(\tau_1\times\tau_2)$, by
  \refrule{T-And we} have $\Gamma,\Sigma\infers t_1:\tau_1$ and
  $\Gamma,\Sigma\infers t_2:\tau_2$. By the induction hypothesis, we also have $\Gamma,\Sigma\infers t_1':\tau_1$ and $\Gamma,\Sigma\infers t_2':\tau_2$.
  This gives us that
  $\Gamma,\Sigma\infers t_1'\And t_2':\Task(\tau_1\times\tau_2)$.\\

  \noindent\textbf{Case} $\userule{S-Next}$ \\
    \indent  Given that
  $\Gamma,\Sigma\infers e_1\Next e_2:\Task \tau$, \refrule{T-Then} gives us that $\Gamma,\Sigma\infers t_1:\Task\tau_1$ and
  $\Gamma,\Sigma\infers e_2:\tau_1 \to \Task \tau$. By the induction hypothesis,
  we know that $t_1\stride t_1'$ preserves and thus
  $\Gamma,\Sigma\infers t_1':\Task\tau_1$. Therefore
  $\Gamma,\Sigma\infers t_1'\Next e_2:\Task\tau$.\\\\

  \noindent\textbf{Case} $\userule{S-OrLeft}$ \\
    \indent  Given that
  $\Gamma,\Sigma\infers t_1\Or t_2:\Task\tau$, by \refrule{T-Or} we have
  $\Gamma,\Sigma\infers t_1:\Task\tau$. By the induction hypothesis, we know that
  $t_1\stride t_1'$ preserves and thus $\Gamma,\Sigma\infers t_1':\Task\tau$.\\

  \noindent\textbf{Case}\\
  $\userule{S-OrRight}$ \\
    \indent  Given that
  $\Gamma,\Sigma\infers t_1\Or t_2:\Task\tau$, by \refrule{T-Or} we have $\Gamma,\Sigma\infers t_2:\Task\tau$. By the induction hypothesis, we know that
  $t_2\stride t_2'$ preserves and thus $\Gamma,\Sigma\infers t_2':\Task\tau$.\\

  \noindent\textbf{Case}\\
  $\userule{S-OrNone}$ \\
    \indent  Given that
  $\Gamma,\Sigma\infers t_1\Or t_2:\Task\tau$, by \refrule{T-Or} we have
  $\Gamma,\Sigma\infers t_1:\Task\tau$ and $\Gamma,\Sigma\infers t_2:\Task\tau$.
  By the induction hypothesis, we know that $t_1\stride t_1'$ and
  $t_2\stride t_2'$ preserve, and thus
  $\Gamma,\Sigma\infers t_1'\Or t_2':\Task\tau$.\\

  \noindent\textbf{Case} $\userule{S-ThenStay}$ \\
    \indent  Given that
  $\Gamma,\Sigma\infers t_1\Then e_2:\Task\tau$,
  by \refrule{T-Then} we have $\Gamma,\Sigma\infers t_1:\Task\tau_1$ and
  $\Gamma,\Sigma\infers e_2:\tau_1\to\Task\tau$. By the induction
  hypothesis, we know that $t_1\stride t_1'$ preserves, and thus
  $\Gamma,\Sigma\infers t_1'\Then e_2:\Task\tau$.\\

  \noindent\textbf{Case}\\
   $\userule{S-ThenFail}$ \\
    \indent  Given that
  $\Gamma,\Sigma\infers t_1\Then e_2:\Task\tau$,
  by \refrule{T-Then} we have $\Gamma,\Sigma\infers t_1:\Task\tau_1$ and
  $e_2:\tau_1\to\Task\tau$. By the induction
  hypothesis, we know that $t_1\stride t_1'$ preserves, and thus
  $\Gamma,\Sigma\infers t_1'\Then e_2:\Task\tau$.\\

  \noindent\textbf{Case}\\
  $\userule{S-ThenCont}$\\
    \indent  Given that
  $\Gamma,\Sigma\infers t_1\Then e_2:\Task\tau$, by \refrule{T-Then} we have
  $\Gamma,\Sigma\infers t_1:\Task\tau_1$ and
  $\Gamma,\Sigma\infers e_2:\tau_1\to\Task\tau$. By the induction hypothesis, we
  know that $t_1\stride t_1'$ preserves. By Lemma~\ref{lem:presvalue}, we know
  that $\Value{(t_1')}=v_1$ preserves. By Theorem~\ref{thm:pres-eval} we know
  that $e_2 v_1\evaluate t_2$ preserves. And finally by the induction hypothesis,
  we know that $t_2\stride t_2'$ preserves. Therefore
  $\Gamma,\Sigma\infers t_2':\Task\tau$.
  %
  % \noindent\textbf{Case} $\userule{S-Appoint}$ Given that
  % $\Gamma,\Sigma\infers u\At t:\Task\tau$, by \refrule{T-Appoint} we have
  % $t:\Task\tau$. By the induction hypothesis, we know that $t,s\stride t',s'$
  % preserves, and thus $\Gamma,\Sigma\infers u\At t':\Task\tau$.\\

@@

\subsubsection{Theorem~\ref{thm:pres-norm}}

@@

\subsubsection{Theorem~\ref{thm:pres-handle}}

@@

  \noindent\textbf{Case} $\userule{H-Change}$\\
  \indent Given that
  $\Gamma,\Sigma\infers\Edit v:\Task\tau$ and $\Sigma\infers s$, the
  \refrule{H-Change} rule additionally gives us that $v,v':\tau$. Therefore by
  \refrule{T-Edit} we have that $\Gamma,\Sigma\infers\Edit v':\Task\tau$\\

  \noindent\textbf{Case} $\userule{H-Empty}$\\
  \indent  Given that
  $\Gamma,\Sigma\infers\Edit v:\Task\beta$ and $\Sigma\infers s$, the
  \refrule{H-Empty} rule additionally gives us that $v:\tau$. Then by
  \refrule{T-Enter} we have $\Gamma,\Sigma\infers\Enter \tau:\Task\tau$ \\

  \noindent\textbf{Case} $\userule{H-Fill}$\\
  \indent  Given that
  $\Gamma,\Sigma\infers\Enter\tau$ and $\Sigma\infers s$, the \refrule{H-Fill}
  rule additionally gives us that $v':\tau$. Then by \refrule{T-Enter} we have
  $\Gamma,\Sigma\infers \Edit v':\Task\tau$.\\

  \noindent\textbf{Case} $\userule{H-Update}$\\
  \indent  Given that
  $\Gamma,\Sigma\infers\Update l:\Task\tau$ and $\Sigma\infers s$. This gives us
  that $\Sigma(l)=\tau$, and we additionally obtain $s(l),v':\tau$ by
  \refrule{H-Update}. By application of Lemma~\ref{lemmasigmaconsistent} this
  case holds.\\

  \noindent\textbf{Case} $\userule{H-PickLeft}$\\
  \indent  Given that
  $\Gamma,\Sigma\infers t_1\Xor t_2:\Task\tau$ and $\Sigma\infers s$, then by
  \refrule{T-Xor} we have $\Gamma,\Sigma\infers t_1:\Task \tau$.\\

  \noindent\textbf{Case} $\userule{H-PickRight}$\\
  \indent  Given that
  $\Gamma,\Sigma\infers t_1\Xor t_2:\Task\tau$ and $\Sigma\infers s$, then by
  \refrule{T-Xor} we have $\Gamma,\Sigma\infers t_2:\Task \tau$. \\

  \noindent\textbf{Case} $\userule{H-Next}$\\
  \indent  Given that
  $\Gamma,\Sigma\infers t_1\Next e_2 :\Task\tau$ and $\Sigma\infers s$. Then by
  \refrule{T-Next}, we have $\Gamma,\Sigma\infers t_1:\Task\tau_1$ and
  $\Gamma,\Sigma\infers e_2:\tau_1\to\Task\tau$. Then by \refrule{T-Then} we
  obtain $\Gamma,\Sigma\infers t_1\Then e_2:\Task\tau$.\\

>>>>

\section{Proofs}

\subsection{Theorem~\ref{thm:pres-eval}}

\begin{proof}
  We prove Theorem~\ref{thm:pres-eval} by induction on $e$:\\

  \case
    {$e=\lambda x:\tau.e, e_1 e_2, x, c, l, e_1 \star e_2,\If{e_1}{e_2}{e_3},\tuple{e_1, e_2},\unit,\Ref e,!e,e_1 := e_2$}
    {Preservation has been proven for these cases by Pierce~\cite{books/Pierce02TAPL}.}

  \case
    {$\userule{E-Edit}$}
    {Given that $\Gamma,\Sigma\infers\Edit e:\Task \tau$ and $\Sigma\infers s$,\refrule{T-Edit} gives us that $\Gamma,\Sigma\infers e:\tau$.
    The induction hypothesis gives us that $e,s\evaluate v,s'$ also preserves, and thus $\Gamma,\Sigma\infers v:\tau$ and $\Sigma\infers s'$.
    Therefore $\Gamma,\Sigma\infers\Edit v:\Task\tau$.}

  \case
    {$\userule{E-Enter}$}
    {Evaluation does not alter $e$ and $s$, therefore this case holds trivially.}

  \case
    {$\userule{E-Update}$}
    {Given that $\Gamma,\Sigma\infers \Edit e:\Task \tau$ and $\Sigma\infers s$, \refrule{T-Update} gives us that $\Gamma,\Sigma\infers e:\Ref \tau$.
    The induction hypothesis gives us that $e,s\evaluate l,s'$ also preserves, and thus $\Gamma,\Sigma\infers l:\Ref\tau$ and $\Sigma\infers s'$.
    Therefore $\Gamma,\Sigma\infers\Update l:\Task\tau$.}

  \case
    {$\userule{E-Fail}$}
    {Evaluation does not alter $e$ and $s$, therefore this case holds trivially.}

  \case
    {$\userule{E-Then}$}
    {Given that $\Gamma,\Sigma\infers e_1\Then e_2:\Task \tau$ and $\Sigma\infers s$, \refrule{T-Then} gives us that $\Gamma,\Sigma\infers e_1:\Task\tau_1$ and $\Gamma,\Sigma\infers e_2:\tau_1 \to \Task \tau$.
    By the induction hypothesis, we know that $e_1,s\evaluate t_1,s'$ preserves and thus $\Gamma,\Sigma\infers t_1:\Task\tau_1$ and $\Sigma\infers s'$.
    Therefore $\Gamma,\Sigma\infers t_1\Then e_2:\Task\tau$.}

  \case
    {$\userule{E-Next}$}
    {Given that $\Gamma,\Sigma\infers e_1\Next e_2:\Task \tau$ and $\Sigma\infers s$, \refrule{T-Next} gives us that $\Gamma,\Sigma\infers e_1:\Task\tau_1$ and $\Gamma,\Sigma\infers e_2:\tau_1 \to \Task \tau$.
    By the induction hypothesis, we know that $e_1,s\evaluate t_1,s'$ preserves and thus $\Gamma,\Sigma\infers t_1:\Task\tau_1$ and $\Sigma\infers s'$.
    Therefore $\Gamma,\Sigma\infers t_1\Next e_2:\Task\tau$.}

  \case
    {$\userule{E-And}$}
    {Given that $\Gamma,\Sigma\infers e_1\And e_2:\Task(\tau_1\times\tau_2)$ and $\Sigma\infers s$, \refrule{T-And} gives us that $\Gamma,\Sigma\infers e_1:\Task\tau_1$ and $\Gamma,\Sigma\infers e_2:\Task\tau_2$.
    By the induction hypothesis, we know that both $e_1,s\evaluate t_1,s'$ and $e_2,s'\evaluate t_2,s''$ preserve and thus $\Gamma,\Sigma\infers t_1:\Task\tau_1$, $\Sigma\infers s'$, $\Gamma,\Sigma\infers t_2:\Task\tau_2$ and $\Sigma\infers s''$.
    Therefore $\Gamma,\Sigma\infers t_1\And t_2:\Task(\tau_1\times\tau_2)$.}

  \case
    {$\userule{E-Or}$}
    {Given that $\Gamma,\Sigma\infers e_1\Or e_2:\Task\tau$ and $\Sigma\infers s$, \refrule{T-Or} gives us that $\Gamma,\Sigma\infers e_1:\Task\tau$ and $\Gamma,\Sigma\infers e_2:\Task\tau$.
    By the induction hypothesis, we have that both $e_1,s\evaluate t_1,s'$ and $e_2,s'\evaluate t_2,s''$ preserve and thus $\Gamma,\Sigma\infers t_1:\Task\tau$, $\Sigma\infers s'$, $\Gamma,\Sigma\infers t_2:\Task\tau$ and $\Sigma\infers s''$.
    Therefore $\Gamma,\Sigma\infers t_1\Or t_2:\Task\tau$.}

  \case
    {$\userule{E-Xor}$}
    {Evaluation does not alter $e$ and $s$, therefore this case holds trivially.}

@@

\subsection{Lemma~\ref{lem:presvalue}}

\begin{proof}
  We prove Lemma~\ref{lem:presvalue} by induction over $e$.\\

\case {$\Value{(\Edit v,s)}=v$}
      {By T-Edit, if $\Gamma,\Sigma\infers \Edit v:\Task\tau$, then $\Gamma,\Sigma\infers v:\tau$.}

\case {$\Value{(\Enter \tau,s)}=\bot$ }
      {Since this case does not lead to a value, the lemma holds trivially.}

\case {$\Value{(\Update l,s)}=s(l)$ }
      {Given that $\Gamma,\Sigma\infers\Update l:\Task \tau$ and $\Sigma\infers s$,
      we know that $\Gamma,\Sigma\infers s(l):\tau$ by definiton.}

\case {$\Value{(\Fail,s)}=\bot$ }
      {Since this case does not lead to a value, the lemma holds trivially.}

\case {$\Value{(t_1\Then e_2,s)}=\bot$}
      { Since this case does not lead to a value, the lemma holds trivially.}

\case {$\Value{(t_2\Next e_2,s)}=\bot$ }
      {Since this case does not lead to a value, the lemma holds trivially.}

\case {$\Value{(t_1\And t_2,s)}=\tuple{v_1, v_2}$ given that $\Value{(t_1,s)}=v_1\wedge\Value{(t_2,s)}=v_2$}
      {By \refrule{T-And} we have that $\Gamma,\Sigma\infers t_1\And t_2:\Task(\tau_1\times\tau_2)$ and $\Gamma,\Sigma\infers t_1:\tau_1$ and $\Gamma,\Sigma\infers t_2:\tau_2$.
      By the induction hypothesis, $ \Value{(t_1,s)}=v_1$ and $\Value{(t_2,s)}=v_2$ preserve, and thus $\Gamma,\Sigma\infers v_1:\tau_1$ and $\Gamma,\Sigma\infers v_2:\tau_2$.
      This gives us that $\Gamma,\Sigma\infers \tuple{v_1, v_2}:\Task(\tau_1\times\tau_2)$.}

\case {$\Value{(t_1\And t_2,s)}=\bot$ given that $\neg(\Value{(t_1,s)}=v_1\wedge\Value{(t_2,s)}=v_2)$}
      { Since this case does not lead to a value, the lemma holds trivially.}

\case
{$\Value{(t_1\Or t_2,s)}=v_1$ given that
  $\Value{(t_1,s)}=v_1$}{
  By \refrule{T-Or} we have that $\Gamma,\Sigma\infers t_1\Or t_2:\Task\tau$,
  and $\Gamma,\Sigma\infers t_1:\Task\tau$ and
  $\Gamma,\Sigma\infers t_2:\Task\tau$. By the induction hypothesis, we have
  that $\Gamma,\Sigma\infers v_1:\tau$.}

\case
{$\Value{(t_1\Or t_2,s)}=v_2$ given that
  $\Value{(t_1,s)}=\bot\wedge\Value{(t_2,s)}=v_2$}{
  By \refrule{T-Or} we have that $\Gamma,\Sigma\infers t_1\Or t_2:\Task\tau$,
  and $\Gamma,\Sigma\infers t_1:\Task\tau$ and
  $\Gamma,\Sigma\infers t_2:\Task\tau$. By the induction hypothesis, we have
  that $\Gamma,\Sigma\infers v_2:\tau$.}

\case
{$\Value{(t_1\Or t_2,s)}=\bot$ given that
  $\Value{(t_1,s)}=\bot\wedge\Value{(t_2,s)}=\bot$}{ Since this case does not
  lead to a value, the lemma holds trivially.}

\case{$\Value{(t_1\Xor t_2,s)}=\bot$ }{Since this case does not
  lead to a value, the lemma holds trivially.}

@@

\subsection{Theorem~\ref{thm:pres-stride}}

\begin{proof}
  We prove Theorem~\ref{thm:pres-stride} by induction on $e$:\\

\case{$\userule{S-Fail}$}
     {Since this case does not alter the expression, the theorem holds trivially.}

\case{$\userule{S-Xor}$}
     {Since this case does not alter the expression, the theorem holds trivially.}

\case{$\userule{S-Update}$}
     {Since this case does not alter the expression, the theorem holds trivially.}

\case{$\userule{S-Fill}$}
     {Since this case does not alter the expression, the theorem holds trivially.}

\case{$\userule{S-Edit}$}
     {Since this case does not alter the expression, the theorem holds trivially.}

\case{$\userule{S-And}$}
     {Given that $\Gamma,\Sigma\infers t_1\And t_2:\Task(\tau_1\times\tau_2)$, by \refrule{T-And we} have $\Gamma,\Sigma\infers t_1:\tau_1$ and $\Gamma,\Sigma\infers t_2:\tau_2$.
     By the induction hypothesis, we also have $\Gamma,\Sigma\infers t_1':\tau_1$ and $\Gamma,\Sigma\infers t_2':\tau_2$.
     This gives us that $\Gamma,\Sigma\infers t_1'\And t_2':\Task(\tau_1\times\tau_2)$.}

\case{$\userule{S-Next}$}
       {Given that
  $\Gamma,\Sigma\infers e_1\Next e_2:\Task \tau$, \refrule{T-Then} gives us that $\Gamma,\Sigma\infers t_1:\Task\tau_1$ and
  $\Gamma,\Sigma\infers e_2:\tau_1 \to \Task \tau$. By the induction hypothesis,
  we know that $t_1\stride t_1'$ preserves and thus
  $\Gamma,\Sigma\infers t_1':\Task\tau_1$. Therefore
  $\Gamma,\Sigma\infers t_1'\Next e_2:\Task\tau$.}

\case{$\userule{S-OrLeft}$}
       {Given that
  $\Gamma,\Sigma\infers t_1\Or t_2:\Task\tau$, by \refrule{T-Or} we have
  $\Gamma,\Sigma\infers t_1:\Task\tau$. By the induction hypothesis, we know that
  $t_1\stride t_1'$ preserves and thus $\Gamma,\Sigma\infers t_1':\Task\tau$.}

\case{$\userule{S-OrRight}$ }
     {Given that $\Gamma,\Sigma\infers t_1\Or t_2:\Task\tau$, by \refrule{T-Or} we have $\Gamma,\Sigma\infers t_2:\Task\tau$.
     By the induction hypothesis, we know that $t_2\stride t_2'$ preserves and thus $\Gamma,\Sigma\infers t_2':\Task\tau$.}

  \case{$\userule{S-OrNone}$}
  {Given that $\Gamma,\Sigma\infers t_1\Or t_2:\Task\tau$, by \refrule{T-Or} we have $\Gamma,\Sigma\infers t_1:\Task\tau$ and $\Gamma,\Sigma\infers t_2:\Task\tau$.
  By the induction hypothesis, we know that $t_1\stride t_1'$ and $t_2\stride t_2'$ preserve, and thus $\Gamma,\Sigma\infers t_1'\Or t_2':\Task\tau$.}

  \case{$\userule{S-ThenStay}$ }
  {Given that $\Gamma,\Sigma\infers t_1\Then e_2:\Task\tau$, by \refrule{T-Then} we have $\Gamma,\Sigma\infers t_1:\Task\tau_1$ and $\Gamma,\Sigma\infers e_2:\tau_1\to\Task\tau$.
  By the induction hypothesis, we know that $t_1\stride t_1'$ preserves, and thus $\Gamma,\Sigma\infers t_1'\Then e_2:\Task\tau$.}

  \case{$\userule{S-ThenFail}$}
  {Given that $\Gamma,\Sigma\infers t_1\Then e_2:\Task\tau$,
  by \refrule{T-Then} we have $\Gamma,\Sigma\infers t_1:\Task\tau_1$ and
  $e_2:\tau_1\to\Task\tau$. By the induction
  hypothesis, we know that $t_1\stride t_1'$ preserves, and thus
  $\Gamma,\Sigma\infers t_1'\Then e_2:\Task\tau$.}

  \case{$\userule{S-ThenCont}$}
  {Given that $\Gamma,\Sigma\infers t_1\Then e_2:\Task\tau$, by \refrule{T-Then} we have
  $\Gamma,\Sigma\infers t_1:\Task\tau_1$ and
  $\Gamma,\Sigma\infers e_2:\tau_1\to\Task\tau$. By the induction hypothesis, we
  know that $t_1\stride t_1'$ preserves. By Lemma~\ref{lem:presvalue}, we know
  that $\Value{(t_1')}=v_1$ preserves. By Theorem~\ref{thm:pres-eval} we know
  that $e_2 v_1\evaluate t_2$ preserves. And finally by the induction hypothesis,
  we know that $t_2\stride t_2'$ preserves. Therefore
  $\Gamma,\Sigma\infers t_2':\Task\tau$.}
  %
  % \noindent\textbf{Case} $\userule{S-Appoint}$ Given that
  % $\Gamma,\Sigma\infers u\At t:\Task\tau$, by \refrule{T-Appoint} we have
  % $t:\Task\tau$. By the induction hypothesis, we know that $t,s\stride t',s'$
  % preserves, and thus $\Gamma,\Sigma\infers u\At t':\Task\tau$.\\

@@

\subsection{Theorem~\ref{thm:pres-norm}}

@@

\subsection{Theorem~\ref{thm:pres-handle}}

@@

  \case
    {$\userule{H-Change}$}
    {Given that $\Gamma,\Sigma\infers\Edit v:\Task\tau$ and $\Sigma\infers s$, the \refrule{H-Change} rule additionally gives us that $v,v':\tau$. Therefore by \refrule{T-Edit} we have that $\Gamma,\Sigma\infers\Edit v':\Task\tau$.}

  \case
    {$\userule{H-Empty}$}
    {Given that $\Gamma,\Sigma\infers\Edit v:\Task\beta$ and $\Sigma\infers s$, the \refrule{H-Empty} rule additionally gives us that $v:\tau$.
    Then by \refrule{T-Enter} we have $\Gamma,\Sigma\infers\Enter \tau:\Task\tau$.}

  \case
    {$\userule{H-Fill}$}
    {Given that $\Gamma,\Sigma\infers\Enter\tau$ and $\Sigma\infers s$, the \refrule{H-Fill} rule additionally gives us that $v':\tau$.
    Then by \refrule{T-Enter} we have $\Gamma,\Sigma\infers \Edit v':\Task\tau$.}

  \case
    {$\userule{H-Update}$}
    {Given that $\Gamma,\Sigma\infers\Update l:\Task\tau$ and $\Sigma\infers s$.
    This gives us that $\Sigma(l)=\tau$, and we additionally obtain $s(l),v':\tau$ by \refrule{H-Update}.
    By application of Lemma~\ref{lemmasigmaconsistent} this case holds.}

  \case
    {$\userule{H-PickLeft}$}
    {Given that $\Gamma,\Sigma\infers t_1\Xor t_2:\Task\tau$ and $\Sigma\infers s$,
    then by \refrule{T-Xor} we have $\Gamma,\Sigma\infers t_1:\Task \tau$.}

  \case
    {$\userule{H-PickRight}$}
    {Given that $\Gamma,\Sigma\infers t_1\Xor t_2:\Task\tau$ and $\Sigma\infers s$,
    then by \refrule{T-Xor} we have $\Gamma,\Sigma\infers t_2:\Task \tau$.}

  \case
    {$\userule{H-Next}$}
    {Given that $\Gamma,\Sigma\infers t_1\Next e_2 :\Task\tau$ and $\Sigma\infers s$.
    Then by \refrule{T-Next}, we have $\Gamma,\Sigma\infers t_1:\Task\tau_1$ and $\Gamma,\Sigma\infers e_2:\tau_1\to\Task\tau$.
    Then by \refrule{T-Then} we obtain $\Gamma,\Sigma\infers t_1\Then e_2:\Task\tau$.}
